Effect of Election on Currency Fluctuation

### 2024-04-14 paper/paper.qmd
added two tables in the data section for better visualization

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

### Construction of Inauguration Week
$$Day1 \hspace{5mm} Day2 \hspace{5mm}  Day3 \hspace{7mm}  Inauguration\ Day \hspace{7mm} Day5 \hspace{5mm} Day6 \hspace{5mm} Day7$$

>>>>

```{r}
#| label: tbl-inauguration
#| tbl-cap: Sample of past inauguration dates information
#| echo: false
cleaned_inauguration <- read_csv(here::here("data/analysis_data/cleaned_inauguration.csv"), show_col_types = FALSE)

knitr::kable(cleaned_inauguration, col.names = c("President", "Party", "Inauguration Date", "Change Party"), align = c("c", "c", "c", "c"))
```

### Construction of Inauguration Week
$$Day1 \hspace{5mm} Day2 \hspace{5mm}  Day3 \hspace{7mm}  \textbf{Inauguration Day} \hspace{7mm} Day5 \hspace{5mm} Day6 \hspace{5mm} Day7$$
```{r}
#| label: tbl-exchange_inaug
#| tbl-cap: Sample of the final dataset used for analysis
#| echo: false
sample_tbl <- exchange_inaug |> filter(date >= "1977-01-12" & date <= "1977-01-18")

knitr::kable(sample_tbl, col.names = c("Date", "Exchange Rate", "Inauguration Period", "Change Party"), align = c("c", "c", "c", "c"))
```
